A meta-analysis of fungicide effects on mungbean powdery mildew

### 2021-05-13 04_Severity_MetaAnalysis.Rmd
can remove restoration of negative numbers now ifelse has been used and the new backtransformation
correct fungicide efficacy calculations

intercept <- round(PMsev_mvSQ$b, 4)[1,1]

# create data.frame
results_mv <- data.frame(
   Moderator = c(
   "Intercept / No Spray control",
   "Early",
   "Late",
   "Late+",
   "Recommended",
   "Recommended+"
   ),
   N = k5,
   k = k6,
   Effect = round(sqrt(abs(PMsev_mvSQ$b)), 4),
   se = round(sqrt(abs(PMsev_mvSQ$se)), 4),
   CI_lower = round(sqrt(abs(PMsev_mvSQ$ci.lb)), 4),
   CI_upper = round(sqrt(abs(PMsev_mvSQ$ci.ub)), 4),
   z_val = round(sqrt(abs(PMsev_mvSQ$zval)), 4),
   p_val = reportP(PMsev_mvSQ$pval, AsNumeric = FALSE, P_prefix = FALSE),
   eff_bar = round(sqrt(abs(1 -(intercept + PMsev_mvSQ$b)/intercept)),4)*100,
   eff_CI_high = round(sqrt(abs(1 -(intercept + PMsev_mvSQ$ci.ub)/intercept)),4)*100,
   eff_CI_low = round(sqrt(abs(1 -(intercept + PMsev_mvSQ$ci.lb)/intercept)),4)*100

@@

# restore negative numbers
results_mv[2:6, c(4,6:8,10:12)] <- -results_mv[2:6, c(4,6:8,10:12)]

@@

disease_estimates_table <-
   flextable(results_mv[c(2,5,6,3,4), c(1:4,6:7, 9:12)]) %>%
   align(j = 2:10, align = "center", part = "all") %>%
   fontsize(size = 8, part = "body") %>%
   fontsize(size = 10, part = "header") %>%
   italic(italic = TRUE, part = "header") %>%
   set_caption(
      "Table 3: Estimated powdery mildew severity mean difference ($u$) to the no spray control (intercept) for each spray schedule treatment. Estimates were calculated from a network meta-analysis of data obtained from grey literature reports of (k) field trials undertaken in Eastern Australia. P values indicate statistical significance in comparison to the intercept."
   ) %>%
   autofit() %>%
   footnote(
      i = 1,
      j = c(2:10),
      value = as_paragraph(
         c(
            "number of treatment means categorised to each spray schedule",
            "number of trials with the respective spray schedule",
            "estimated mean yield determined by the meta-analysis",
            "Lower range of the 95% confidence interval",
            "Upper range of the 95% confidence interval",
            "indicates the significance between each respective spray schedule and the no spray control (intercept)",
            "Fungicide spray schedule efficacy",
            "Lower range of the 95% confidence interval",
            "Upper range of the 95% confidence interval"
         )
      ),
      ref_symbols = letters[c(1:7,4,5)],
      part = "header",
      inline = TRUE
   )%>%
   add_header(Moderator = "",
              N = "",
              k = "",
              mu = "Effect Size",
              `CI_{L}` = "Effect Size",
              `CI_{U}` = "Effect Size",
              P  = "Effect Size",
              Efficacy = "PM control",
              `Eff CI_lower` = "PM control",
              `Eff CI upper` = "PM control") %>%
   merge_h( part = "header")%>%
   hline_top(part="all", border = officer::fp_border(color = "black", width = 2) )

>>>>

intercept <- PMsev_mvSQ$b[1,1]

# create data.frame
results_mv <- data.frame(
   Moderator = c(
      "Intercept / No Spray control",
      "Early",
      "Late",
      "Late+",
      "Recommended",
      "Recommended+"
   ),
   N = k5,
   k = k6,
   Effect = ifelse(PMsev_mvSQ$b == intercept, sqrt(intercept),
                   round(
                      sqrt(PMsev_mvSQ$b + intercept) - sqrt(intercept), 4
                   )),
   se = round(
      sqrt(
         ifelse(PMsev_mvSQ$b == intercept, intercept,
                PMsev_mvSQ$b + intercept) + PMsev_mvSQ$se) -
         sqrt(
            ifelse(PMsev_mvSQ$b == intercept, intercept,
                   PMsev_mvSQ$b + intercept)),
      4),
   CI_lower = round(sqrt(PMsev_mvSQ$ci.lb + intercept) - sqrt(intercept), 4),
   CI_upper = round(sqrt(PMsev_mvSQ$ci.ub + intercept) - sqrt(intercept), 4),
   z_val = round(PMsev_mvSQ$zval, 4),
   p_val = reportP(PMsev_mvSQ$pval, AsNumeric = FALSE, P_prefix = FALSE))

results_mv <- 
   results_mv %>%
   mutate(
   eff_bar = round(
      1 - (sqrt(intercept) + Effect) /
              sqrt(intercept), 
      4) * 100,
   eff_CI_high = round(
      1 - (sqrt(intercept) + CI_upper) / sqrt(intercept)
   , 4) * 100,
   eff_CI_low = round(
      1 - (sqrt(intercept) + CI_lower) / sqrt(intercept)
   , 4) * 100

@@

# remove efficacy in control
results_mv[1,10:12] <- NA

@@

disease_estimates_table <-
   flextable(results_mv[c(2,5,6,3,4), c(1:7, 9:12)]) %>%
   align(j = 2:10, align = "center", part = "all") %>%
   fontsize(size = 8, part = "body") %>%
   fontsize(size = 10, part = "header") %>%
   italic(italic = TRUE, part = "header") %>%
   set_caption(
      "Table 3: Estimated powdery mildew severity mean difference ($u$) to the no spray control (intercept) for each spray schedule treatment. Estimates were calculated from a network meta-analysis of data obtained from grey literature reports of (k) field trials undertaken in Eastern Australia. P values indicate statistical significance in comparison to the intercept."
   ) %>%
   autofit() %>%
   footnote(
      i = 1,
      j = c(2:4,6:11),
      value = as_paragraph(
         c(
            "number of treatment means categorised to each spray schedule",
            "number of trials with the respective spray schedule",
            "estimated mean yield determined by the meta-analysis",

            "Lower range of the 95% confidence interval",
            "Upper range of the 95% confidence interval",
            "indicates the significance between each respective spray schedule and the no spray control (intercept)",
            "Fungicide spray schedule efficacy",
            "Lower range of the 95% confidence interval",
            "Upper range of the 95% confidence interval"
         )
      ),
      ref_symbols = letters[c(1:7,4,5)],
      part = "header",
      inline = TRUE
   )%>%
   add_header(Moderator = "",
              N = "",
              k = "",
              mu = "Effect Size",
              se = "Effect Size",
              `CI_{L}` = "Effect Size",
              `CI_{U}` = "Effect Size",
              P  = "Effect Size",
              Efficacy = "PM control",
              `Eff CI_lower` = "PM control",
              `Eff CI upper` = "PM control") %>%
   merge_h( part = "header")%>%
   hline_top(part="all", border = officer::fp_border(color = "black", width = 2) )
